PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-05 paper/app-pineappl.tex
Add small changes

\paragraph{Channels and Luminosity function.}
Sometimes it is useful to know which partons contribute the most and by how much.
This is what the subcommand \texttt{channels} shows:
\begin{verbatim}
 $ pineappl channels ATLASZHIGHMASS49FB.pineappl \
 > NNPDF31_nlo_as_0118_luxqed --limit 5
bin xmin xmax lumi  size
---+----+----+----+------+---+------+---+------+---+------+---+-----
  0  116  130  #15 27.42%  #0 27.42%  #5 24.52% #20 24.51% #30 1.30%
  1  130  150  #15 28.83%  #0 28.83%  #5 21.78% #20 21.78% #30 1.86%
  2  150  170  #15 29.87%  #0 29.82%  #5 19.63% #20 19.62% #30 2.32%
  3  170  190  #15 30.54%  #0 30.53% #20 18.17%  #5 18.13% #30 2.58%
  4  190  210   #0 31.06% #15 31.04%  #5 17.07% #20 17.04% #30 2.75%
  5  210  230   #0 31.46% #15 31.38% #20 16.27%  #5 16.24% #30 2.86%
  6  230  250   #0 31.73% #15 31.64% #20 15.66%  #5 15.62% #30 2.91%
  7  250  300   #0 32.07% #15 32.02%  #5 14.91% #20 14.86% #30 2.98%
  8  300  400   #0 32.62% #15 32.56%  #5 13.83% #20 13.81% #30 2.98%
  9  400  500  #15 33.14%  #0 33.12% #20 12.89%  #5 12.87% #30 2.93%
 10  500  700   #0 33.71% #15 33.31% #20 12.28%  #5 12.26% #30 2.93%
 11  700 1000  #15 34.08%  #0 33.71% #20 11.59%  #5 11.51% #30 3.06%
 12 1000 1500   #0 33.95% #15 33.88% #20 11.12%  #5 10.88% #30 3.56%
\end{verbatim}
The first three columns are known from \texttt{convolute}.
The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then relative size of the corresponding contribution.
Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0}, then \texttt{\#5}, etc.
The meaning of the channel numbers is given by using the subcommand \texttt{luminosity} (only an excerpt is shown):
\begin{verbatim}
id    entry
--+------------+------------+------------
0  1 × ( 2, -2) 1 × ( 4, -4)
5  1 × ( 1, -1) 1 × ( 3, -3)
15 1 × (-4,  4) 1 × (-2,  2)
20 1 × (-3,  3) 1 × (-1,  1)
30 1 × (22, 22)
\end{verbatim}
This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contribution (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
The factors \texttt{1} are not important here, but in general they can contain CKM matrix elements that would otherwise not allow to share the matrix elements between different quark flavours.

>>>>

\paragraph{Channels and Luminosity function.}
Sometimes it is useful to know which partons contribute the most and by how much.
This is what the subcommand \texttt{channels} shows:
\begin{verbatim}
 $ pineappl channels ATLASZHIGHMASS49FB.pineappl \
 > NNPDF31_nlo_as_0118_luxqed --limit 5
bin xmin xmax lumi  size
---+----+----+----+------+---+------+---+------+---+------+---+-----
  0  116  130  #15 27.42%  #0 27.42%  #5 24.52% #20 24.51% #30 1.30%
  1  130  150  #15 28.83%  #0 28.83%  #5 21.78% #20 21.78% #30 1.86%
  2  150  170  #15 29.87%  #0 29.82%  #5 19.63% #20 19.62% #30 2.32%
  3  170  190  #15 30.54%  #0 30.53% #20 18.17%  #5 18.13% #30 2.58%
  4  190  210   #0 31.06% #15 31.04%  #5 17.07% #20 17.04% #30 2.75%
  5  210  230   #0 31.46% #15 31.38% #20 16.27%  #5 16.24% #30 2.86%
  6  230  250   #0 31.73% #15 31.64% #20 15.66%  #5 15.62% #30 2.91%
  7  250  300   #0 32.07% #15 32.02%  #5 14.91% #20 14.86% #30 2.98%
  8  300  400   #0 32.62% #15 32.56%  #5 13.83% #20 13.81% #30 2.98%
  9  400  500  #15 33.14%  #0 33.12% #20 12.89%  #5 12.87% #30 2.93%
 10  500  700   #0 33.71% #15 33.31% #20 12.28%  #5 12.26% #30 2.93%
 11  700 1000  #15 34.08%  #0 33.71% #20 11.59%  #5 11.51% #30 3.06%
 12 1000 1500   #0 33.95% #15 33.88% #20 11.12%  #5 10.88% #30 3.56%
\end{verbatim}
The first three columns are known from \texttt{convolute}.
The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then relative size of the corresponding contribution.
Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0}, then \texttt{\#5}, etc.
The meaning of the channel numbers is given by using the subcommand \texttt{luminosity} (only an excerpt is shown):
\begin{verbatim}
id    entry
--+------------+------------+------------
0  1 × ( 2, -2) 1 × ( 4, -4)
5  1 × ( 1, -1) 1 × ( 3, -3)
15 1 × (-4,  4) 1 × (-2,  2)
20 1 × (-3,  3) 1 × (-1,  1)
30 1 × (22, 22)
\end{verbatim}
This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contributions (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with its initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
The size of the remaining channels is smaller than the photon--photon channel.
The factors \texttt{1} are not important here, but in general they can contain CKM values that, if kept in the squared matrix elements, would not allow to share a single matrix elements for different quark flavours and therefore slow down the calculation.

### 2020-08-05 paper/paper.tex
fast-interpolation in the abstract
Add small changes

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanations about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data. \\
%Alessandro Vicini\\
E.R.N. is supported by the European Commission through the Marie
Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
C.S.\ is supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.

>>>>

\acknowledgments
We are grateful to Rikkert Frederix for discussions and explanations about
\textsc{aMCfast}. We acknowledge discussions with 
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data. \\
%Alessandro Vicini\\
%Stefan Dittmaier
E.R.N. is supported by the European Commission through the Marie
Sk\l odowska-Curie Action ParDHonS FFs.TMDs (grant number 752748).
C.S.\ and S.C.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
MZ thanks the Nikhef institute in Amsterdam,
where he was employed during the early stages of this paper.
